\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS 5}
\author{Jack Wang}

\begin{document}
\maketitle


\section{Question 3}

The data is the University Ranking for financial archival accounting research provided by BYU. 
This ranking is very important in accounting academia because it is widely accepted as a reflection of accounting research level of each university. This may help me to identify my ideal and reasonable target when I am on job market. 
I scrape the data based on your instruction in class. The data on the webpage is clearly presented and is easy to parse.

\section{Question 4}

The data I scraped with API method is the XBRL format financial data for listed companies. This data is directly from financial reports of the filing of each listed company with a unified tag for most of the information. This data is really useful considering there are a lot of errors for financial data in commercial database and there data collection process is basically a black box for researchers. This data set provide with correct clean data for accounting research.
I used jsonlite and tidyverse for data collecting.

\end{document}